---
title: "hmwrk_wk4"
author: "Lorena Brambila"
date: "11/12/2021"
output: html_document
---

# Inequality task - week 4

## Reproduce

### package versions

```{r first, eval=FALSE}
#this it to load all packages used in code with the version when this was developed
#i have taken a snapshot with
renv::snapshot()

#install the same packages
renv::restore()
```

### Read in data:

Located within the Data folder:
(this is good practice so people can download the data you are using)
*HDI data from: http://hdr.undp.org/en/indicators/68606#
*Shapefile from: https://hub.arcgis.com/datasets/2b93b06dc0dc4e809d3c8db5cb96ba69_0/explore?location=-0.047158%2C0.000000%2C1.00

## Load packages
```{r}
library(tidyverse)
library(sf)
library(here)
library(janitor)
library(countrycode)
```

##Read data in 
```{r}
HDI <- read_csv(here::here("Data", "Gender Inequality Index (GII).csv"),
                locale = locale(encoding = "latin1"),
                na = "..", skip=5)
#na = ".." to exclude not available data from csv and skip = 5 because the first 5 rows are headings
World <- st_read(here::here("Data", "World_Countries__Generalized_.shp"))
```

## Column names

Select columns we want and change country name to country code, using the 'country code' package

We could also just join it without this on the country name column

```{r}
HDIcols<- HDI %>%
  clean_names()%>% #removes all capitals and spaces
  select(country, x2019, x2010)%>%
  mutate(difference=x2019-x2010)%>%
  slice(1:189,)%>% #we look at data set and get rid of the rows we don't want with slice / , is for columns
  mutate(iso_code=countrycode(country, origin = 'country.name', destination ='iso2c'))

```

## Join

Join the csv to world shape file 

```{r}
Join_HDI <- World %>%
  clean_names() %>%
  left_join(.,
            HDIcols,
            by = c("aff_iso" = "iso_code"))
```

